Supplement 2: Stationwise Evaluation

### 2018-09-29 pkg/disttree/inst/draft/supplement/supplement_stationwise.Rnw
more work on supplements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2299 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 42375fce433cf91b5ec4e546daaa344ee5df0bc4

\item \emph{EMOS} \citep{Gneiting+Raftery+Westveld:2005}: 
Standard ensemble model output statistics uses the ensemble 
mean of total precipitation as regressor in the location submodel 
and the corresponding ensemble standard deviation in the scale submodel.
The parameters are estimated by maximum likelihood.

>>>>

\item \emph{EMOS} \citep{Gneiting+Raftery+Westveld:2005}: 
Ensemble model output statistics uses the ensemble 
mean of total precipitation as regressor in the location submodel 
and the corresponding ensemble standard deviation in the scale submodel.
The parameters are estimated by maximum likelihood.
